Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-08-28 paper/paper.tex
wrote text in Mannik and stadium shape section Tested everything on quipu.

\section{Comparison of Mannik's Experimental and Our Stadium Shapes}
We have made and studied different plots and movies that show the
change in concentration of MinD over time We have found that the
deterministic simulations of the protein reaction sequence discussed
above results in robust oscillatory behavoir of polar selection and
oscillation in a wide variety of cell shapes.  This differs with
Mannik's experimental findings that show much less regular behavoir,
with a large variation in the location of maxima.  On the other hand,
our stochastic simulations show irregular behavoir in the irregular
shapes and more regular, pole to pole oscillations in the pill and
stadium shaped cells.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{../paper/plot-ave}
  \caption{Arrows depicting global maxima in space and local maxima in
    time overlayed on color plots of time averaged total MinD density.
    At this point the data is over varying amounts of time but its all
    roughly 1000 seconds\fixme{fix this}.  The top row shows plots
    published by Mannik of the MinD maxima behavoir and the bottom two
    rows show our pancake shapes that are designed to have the same
    shape.  The middle row shows results from the stochastic
    simulation and the bottom shows results from the deterministic.
    We can see that the stochastic method shows behavoir that is
    similar to experiment while the deterministic method shows
    maximization that is too regular and robust.}
  \label{randst-plot-ave}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
  \caption{Arrows depicting global maxima in space and local maxima in
    time overlayed on color plots of time averaged total MinD
    density.\fixme{how much of time of data is shown?}.  Although
    there is variation in the specific location of maxima on each edge
    of the cell, the behavoir for both of these regular shapes is
    robust and exhibits a back and forth oscillatory manner.  The
    wildtype pill shape behavoir matches well with experiment.
    Regular pancake shapes have not been observed experimentally, but
    our stochastic simulations would suggest that they would exhibit
    regular robust oscillations similar to the pill shapes.  This is
    in contrast to the behavoir of Mannik cells seen in
    Figure~{randst-plot-ave}}
  \label{arrow-pill-stadium}
\end{figure}

>>>>

\section{Comparison of Mannik's Experimental and Our Stadium Shapes}
We have made and studied different types of plots and movies that show
the change in concentration of MinD over time. We have found that the
deterministic simulations of the protein reaction sequence discussed
above results in robust oscillatory behavoir of polar selection and
oscillation in a wide variety of cell shapes.  This differs with
Mannik's experimental findings that show much less regular behavoir,
with a large variation in the location of maxima.  On the other hand,
our stochastic simulations show irregular behavoir in the irregular
shapes and more regular, pole to pole oscillations in the pill and
stadium shaped cells, agreeing well with Mannik's experimental
findings.

Figure~{arrow-pill-stadium} and Figure~{randst-plot-ave} show color
plots of time-averaged MinD overlayed by arrows depicting sequential
maxima that are global in space and local in time.  Our shapes that
designed to look like Mannik cells show well the inadequacy of the
deterministic method of simulation and conversely the accuracy of the
stochastic method.  The stochastic method movies (and arrow plots of
Figure~{randst-plot-ave}) show irregular location of maxima that is
similar to what is observed experimentally by Mannik. There is a
general bias towards back and forth behavoir, which can be seen in the
box plots of Figure~{box-mannik}, but the behavoir is irregular and
the location of the maxima vary a significant amount.  On the other
hand, the deterministic simulations show behavoir that is much too
regular, exhibiting locations of maxima that do not vary.  The
deterministic method is seen to be inadequate.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{../paper/plot-ave}
  \caption{Arrows depicting global maxima in space and local maxima in
    time overlayed on color plots of time averaged total MinD density.
    A density threshold is chosen and only maxima above this threshold
    are shown. The plots serve to illistrate what is observed in our
    movies.  At this point the data is over varying amounts of time
    but its all roughly 1000 seconds\fixme{fix this}.  The top row
    shows plots published by Mannik of the MinD maxima behavoir and
    the bottom two rows show our pancake shapes that are designed to
    have the same shape.  The middle row shows results from the
    stochastic simulation and the bottom shows results from the
    deterministic.  We can see that the stochastic method shows
    behavoir that is similar to experiment while the deterministic
    method shows maximization that is too regular and robust.}
  \label{randst-plot-ave}
\end{figure}

Our simulations of pill shapes show behavoir that is once again well
matched by experiment, but this time the deterministic method seems to
be as aduaquet as the stochastic in giving accurate results.  The
experimental cells show regular back and forth behavoir, as do both
simulations.  In this case the natural bias of the deterministic
method towards robustness and regularity works in its favor.

Judging that at this point that we have a fair idea of how our two
methods compare in terms of experimental acuracy, we are intersted to
investigate the limits of the break down of regular activity, by
simulating large, regular, 'stadium' shapes.  These shapes have the
flattened, pancake like form of our irregularly shaped cells, but from
the top down they look as pills do. In two dimensions they are
composed of a rectangle with two half ellipse connected on either end.
They are also made to have a large volume similar to the Mannik
shapes.

We find that both the stochastic and the deterministic solutions show
regular show back and forth behavoir in the stadium shaped cells, as
can be seen Figure~{box-stadium}.  This suggests that it is the
irregular shape of the Mannik cells,, not the size or their flattened
nature, that causes these cells be exhibit irregularity in MinD
oscillations.

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
  \caption{Arrows depicting global maxima in space and local maxima in
    time overlayed on color plots of time averaged total MinD
    density. A density threshold is chosen and only maxima above this
    threshold are shown. The plots serve to illistrate what is
    observed in our movies. \fixme{how much of time of data is
      shown?}.  Although there is variation in the specific location
    of maxima on each edge of the cell, the behavoir for both of these
    regular shapes is robust and exhibits a back and forth oscillatory
    manner.  The wildtype pill shape behavoir matches well with
    experiment.  Regular pancake shapes have not been observed
    experimentally, but our stochastic simulations would suggest that
    they would exhibit regular robust oscillations similar to the pill
    shapes.  This is in contrast to the behavoir of Mannik cells seen
    in Figure~{randst-plot-ave}}
  \label{arrow-pill-stadium}
\end{figure}

@@
